### 2020-06-29 mycv/subs/papers.tex
Updates in diffraction.ipynb

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C N. Tom\'{e}}
  {An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}
  {}
  {Submitted for publication}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, D Steglich}
  {Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}
  {International Journal of Mechanical Sciences}
  {Accepted for publication}
  {
  }

>>>>

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % % ---------------------------------------------------------
  % \cventry
  % {\underline{Y. Jeong}$^*$, C N. Tom\'{e}, B. Jeon}
  % {Finite element analysis of incremental elasto-visco-plastic self-consistent polycrystal model}
  % {}
  % {in preparation}
  % {
  % }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C N. Tom\'{e}}
  {An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}
  {International Journal of Plasticity}
  {In Press}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, D Steglich}
  {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
  {International Journal of Mechanical Sciences}
  {Vol. 181, 105680, 2020}
  {
  }

### 2020-06-29 mycv/subs/skills.tex
Updates
Updates in diffraction.ipynb

  \cvskill
  {Digital Image Correlation (DIC)}
  {VIC3D}

@@

  \cvskill
  {Computer skills}
  {Linux, Git, Abaqus (UMAT and Python script), Parallel computation}

  \cvskill
  {Constutitive modelling}
  {Macro-mechanical description for anisotropic metals using anisotropic yield functions}

  \cvskill
  {Crystal plasticity}
  {Viscoplastic self-consistent (VPSC) and Elasto-viscoplastic self-consistent crystal plasticity models}

>>>>

  \cvskill
  {Digital Image Correlation (DIC)}
  {VIC3D, DICE}

@@

  \cvskill
  {Computer skills}
  {Linux, Git, Parallel computation}

  \cvskill
  {Constitutive modelling}
  {Macro-mechanical description on anisotropic metals using anisotropic yield functions}

  \cvskill
  {Crystal plasticity}
  {Visco-plastic / Elasto-visco-plastic self-consistent crystal plasticity models}
